---
title: "Run DaNCES Simulations"
author: "Marina Papadopoulou"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Run Simulations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette intends to guide the user through setting up a simulation experiment using a model built with the DaNCES software. For a working example of its functionality, see the [DaNCES_simulator](https://github.com/marinapapa/DaNCES_simulator) repo.

## Step 1. Repository set up

The `rDaNCES` package first defines a set of directories that will be used for keeping your repository tidy while running simulation experiments.
First, we need to define a name for our experiment and give the path to the folder that contains the executable (.exe) of our agent-based simulation:

```{r message=FALSE, warning=FALSE}

exp_name <- 'rdances_demo' ## choose a name for the experiment
model_exe_path <- '..\\simulator\\sim_demo\\dances.exe' ## adjust accordingly

```

The model executable should be in a separate folder in our working directory to be further used as the main repository for our simulations runs.
Most importantly, a template config (here named "demo_config.json") corresponding to the executable should be given: 

```{r message=FALSE, warning=FALSE}

main_repo <- dirname(model_exe_path)
config_tmp_name <- paste0(main_repo, '/config.json')

```
The package uses these paths to set up a directory with the name of our experiment that contain the following: 

1. The 'generated_configs' subdirectory that will contain all the configuration files that cover the parameter space we go through with the experiment.
2. A log file with the text outputs of the loop over the parameter space for simulation runs.
3. A potential results folder that also includes a copy of the investigated parameter space in a *tmp* subdirectory.


```{r message=FALSE, warning=FALSE}

library(rDaNCES)
## Note: uncomment the following call when you have the model exe file in the defined directory.
# dirs <- set_up_directories(sim_name = exp_name,
#                            config_name = config_tmp_name,
#                            model_exe = model_exe_path,
#                            main_path =  main_repo
#                            )

```

## Step 2. Parameter space set up

Now we can define which parameters we want to vary across our simulations, construct a parameter set, and set how many repetitions of each parameter combination we want. For a list of which parameters can be changed with the current version of the software see the parameters_class.R help file.

```{r message=FALSE, warning=FALSE}

### Parameter values
N <- c(5, 10, 20) # group size of prey
speed <- c(5, 10) # cruise speed of prey

# Number of repetitions of each parameter set:
reps <- 2

## Set up parameter combinations
param_set <- construct_ParamSets(
    N = N, 
    fl_aer_cs = speed, 
    output_folder = exp_name
  )
  
```

## Step 3. Simulation set up & run

Using our parameter set and directories, we can produce the new configuration files and run the simulations:

```{r message=FALSE, warning=FALSE}

## Create configuration files 
## Note: uncomment the following line when you have set the configuration template file in the defined directory.
#set_up_simulations(param_set, dirs)

#print(paste0('We will run ', length(list.files(dirs$EXP_CONFIGS_PATH)) * reps, ' simulations.'))

```
So when we are ready, we can run the simulations. The function will create a folder with the simulated data in the parent repository of the main folder:

```{r message=FALSE, warning=FALSE}
## Run all simulation
## Note: uncomment the following line when you have set the model exe file in the defined directory.
#run_simulations(dirs, reps)

```

## Step 4. Import the simualted output

After the simulations have run successfully, we can use the package's functions to load the simulated data and configuration, depending on the analysis observers we have set:

```{r message=FALSE, warning=FALSE}
## Load output of a single simulation. Each set of csv files from a simulation is saved in a uniquely named folder:
output_path <- '../sim_data/rdances_demo/21749914392644'

## Note: uncomment the following line when you have generated the data. 
#sim_data <- import_base_data(output_path, types = c("self", "group"))


## Or load the output of the full experiment: 
output_path <- '../sim_data/rdances_demo/'

## Note: uncomment the following line when you have generated the data. 
#sim_data_all <- import_multi_data(output_path, types = c("self", "group"))

```

